QALY Comparison - Living Wage Intervention

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Added a function to calculate the total cost of the intervention (int - baseline). Also fixed the QALY calculation as there was a small mistake (pointed to MCS instead of PCS in one leg of the calculation)

```{r}
#ICER <- function(base, base.name, int, int.name, QALY_value) {

base <- noSupport
base.name <- 'energyDownliftNoSupport'
int <- support
int.name <- 'energyDownlift'
QALY_value <- 60000

combined <- rbind(base, int)

combined.cost.mean <- combined %>%
  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * QALY_value) %>%
  group_by(run_id, year, intervention) %>%
  summarise(across(everything(), mean))

# ICER = (C1 - C0) / (E1 - E0)
# where
# C1 = cost of intervention
# E1 = effect of intervention
# C0 = cost of control group
# E0 = effect of control group

# prepare var names
c1 <- paste('total_boost', int.name, sep='_')
c0 <- paste('total_boost', base.name, sep='_')
e1 <- paste('QALYs', int.name, sep='_')
e0 <- paste('QALYs', base.name, sep='_')

ICER <- combined.cost.mean %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (.data[[c1]] - .data[[c0]]) / (.data[[e1]] - .data[[e0]])) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = int.name)

pc1 <- quantile(ICER$ICER, .01)
print(pc1)
print(min(ICER$ICER))
pc99 <- quantile(ICER$ICER, .99)
print(pc99)
print(max(ICER$ICER))

ICER <- filter(ICER, ICER < pc99, ICER > pc1)
print(min(ICER$ICER))
print(max(ICER$ICER))

p1 <- ggplot(ICER, aes(x = year, y = ICER, group = intervention, fill = intervention, colour = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name))
print(p1)

ICER.final <- ICER %>%
  group_by(run_id, intervention) %>%
  summarise(ICER = mean(ICER)) %>%
  group_by(intervention) %>%
  summarise(margin = (qt(0.975, df=n() - 1) * sd(ICER)) / sqrt(n()),
            ICER = mean(ICER))

p2 <- ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = ICER - margin, ymax = ICER + margin, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = paste0(int.name, ' vs ', base.name)) +
  xlab('Intervention')
print(p2)

print(paste0('ICER == ', ICER.final$ICER, ' +- ', ICER.final$margin))
```

>>>>

# Total Cost of Intervention

```{r}
intervention.cost(base = noSupport,
                  base.name = 'energyDownliftNoSupport',
                  int = support,
                  int.name = 'energyDownlift',
                  int.label = 'EPCG')
```

### 2023-11-14 minos/testing/QALY_comparison_livingWage.Rmd
Added a function to calculate the total cost of the intervention (int - baseline). Also fixed the QALY calculation as there was a small mistake (pointed to MCS instead of PCS in one leg of the calculation)

Can check histogram over each run to see the range of QALYs.

```{r}
# # histogram of qalys
# ggplot(combined, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
# 
# ggplot(filter(combined, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALYs by run', subtitle = '2022')
# 
# ggplot(filter(combined, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALYs by run', subtitle = '2028')
# 
# ggplot(filter(combined, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALYs by run', subtitle = '2034')
```

and histograms of change...

```{r}
# # histogram of qalys
# ggplot(combined.QALY.change, aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
# 
# ggplot(filter(combined.QALY.change, year == 2022), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALY change by run', subtitle = '2022')
# 
# ggplot(filter(combined.QALY.change, year == 2028), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALY change by run', subtitle = '2028')
# 
# ggplot(filter(combined.QALY.change, year == 2034), aes(x = QALYs, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'QALY change by run', subtitle = '2034')
```

...and SF_12 MCS and PCS for good measure.

```{r}
# ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention)) +
#   geom_smooth()
# 
# ggplot(combined, aes(x = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
# 
# ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention)) +
#   geom_smooth()
# 
# ggplot(combined, aes(x = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year)
```

@@

```{r}
cost.per.qaly(base = base,
              base.name = 'baseline',
              int = wage,
              int.name = 'livingWageIntervention',
              QALY_value = 60000)  # QALY value == £60,000
```

```{r}
# total.combined.cost <- combined.cost.change %>%
#   group_by(run_id, intervention) %>%
#   summarise(TotalChange = sum(QALY_value_change)) %>%
#   group_by(intervention) %>%
#   summarise(se = sd(TotalChange) / sqrt(n()),
#             TotalChange = mean(TotalChange))
# 
# #print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))
# 
# ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
#   geom_col() +
#   geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
#   scale_y_continuous(label = comma) +
#   labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
#   xlab('Intervention')
# 
# ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year) +
#   labs(title = 'QALY value change')
```

@@

```{r}
ICER(base = base,
     base.name = 'baseline',
     int = wage,
     int.name = 'livingWageIntervention',
     QALY_value = 60000)
```

```{r}
# ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year) +
#   labs(title = 'ICER by run', subtitle = 'All Years')
# 
# ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2022')
# 
# ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2028')
# 
# ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2031')
# 
# ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2034')
```

>>>>

@@

```{r}
cost.per.qaly(base = base,
              base.name = 'baseline',
              int = wage,
              int.name = 'livingWageIntervention',
              QALY_value = 60000,
              int.label <- 'LivingWage')  # QALY value == £60,000
```

@@

```{r}
ICER(base = base,
     base.name = 'baseline',
     int = wage,
     int.name = 'livingWageIntervention',
     QALY_value = 60000,
     int.label = 'LivingWage')
```

# Total Cost of Intervention

```{r}
intervention.cost(base = baseline,
                  base.name = 'baseline',
                  int = livWage,
                  int.name = 'livingWageIntervention',
                  int.label = 'Living Wage')
```
